\LARGE How coexistence mechanisms mediate temporal stability

### 2014-11-04 manuscript/ms_CoexistStability.Rnw
notated code
updated initial condition for V for readablity

At the beginning of each season we start with initial conditions defined as $V_{t}$, $W_{t}$, and $Z_{t}$ for the dormant state, the live state, and the resource, respectively. So for each season, Eqs. 1-3 are solved given the initial conditions:
\begin{align}
  D_{i}(0) &= V_{i,t} \\
  N_{i}(0) &= W_{i,t} \\
  R(0) &= Z_{t}
\end{align}
The consumers transition between $N$ and $D$ instantaneously between years. We assume resource density does not change between years. So, at the yearly transition:
\begin{align}
  V_{i,t+1} &= D_{i}(T^-) + N_{i}(T^-) - [N_{i}(T^-)+D_{i}(T^-)]g_{t} \\
  W_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)]g_{t} \\
  Z_{t+1} &= R(T^-)
\end{align}
where $D(T^-)$, $N(T^-)$, and $R(T^-)$ are the densities of each state at the end of the year and $g$ is a time-fluctuating activation rate that regulates how much dormant biomass is converted to growing-season live biomass each year. Our formulation assumes that at the end of each season all accumulated living biomass [$N(T^-)$] is converted to dormant biomass.

@@

@@

>>>>

At the beginning of each season we start with initial conditions defined as $V_{t}$, $W_{t}$, and $Z_{t}$ for the dormant state, the live state, and the resource, respectively. So for each season, Eqs. 1-3 are solved given the initial conditions:
\begin{align}
  D_{i}(0) &= V_{i,t} \\
  N_{i}(0) &= W_{i,t} \\
  R(0) &= Z_{t}
\end{align}
The consumers transition between $N$ and $D$ instantaneously between years. We assume resource density does not change between years. So, at the yearly transition:
\begin{align}
  V_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)](1-g_{t}) \\
  W_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)]g_{t} \\
  Z_{t+1} &= R(T^-)
\end{align}
where $D(T^-)$, $N(T^-)$, and $R(T^-)$ are the densities of each state at the end of the year and $g$ is a time-fluctuating activation rate that regulates how much dormant biomass is converted to growing-season live biomass each year. Our formulation assumes that at the end of each season all accumulated living biomass [$N(T^-)$] is converted to dormant biomass.

\begin{center}
\begin{table}
\caption{Definition of model parameters.}
\begin{tabular}{l l}
\hline
Parameter & Definition \\
\hline
$m_{D}$ & dormant state mortality rate \\
$r$ & live state maximum resource uptake rate \\
$K$ & live state half-saturation constant for resource uptake rate \\
$m_{N}$ & live state mortality rate \\
$a$ & resource turnover rate \\
$S$ & resource supply rate \\
$g$ & dormant-to-live biomass transition fraction \\ 
\hline
\end{tabular}
\end{table}
\end{center}

@@

Following Adler and Drake (2008), we generated sequences of (un)correlated dormant-to-live state transition rates ($g$) for each species by drawing from multivariate normal distributions with mean 0 and a variance-covariance matrix of

\begin{align}
\begin{bmatrix}
\sigma^2_{E} & \rho\sigma^2_{E} \\
\rho\sigma^2_{E} & \sigma^2_{E}
\end{bmatrix}
\end{align}

\noindent{}where $\sigma^2_{E}$ is the variance and $\rho$ is the correlation between between the two species' transition rates. For environmental variability, here induced as variability in $g$, to promote coexistence via the storage effect, $\rho$ must be less than 1. The inferior competitor has the strongest potential to persist when $\rho=-1$ (perfectly uncorrelated transition rates).

@@

NOTE: I should probably also put a check in the code somewhere to make sure we don't have extinctions...
